Global patterns of forest autotrophic carbon fluxes

### 2020-10-27 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

We found no evidence of systematic variation in C allocation with latitude or climate (Fig. S3). Of 12 relationships tested (3 ratios among C flux variables regressed against latitude, $MAT$, $MAP$ and temperature seasonality), none were significant.

>>>>

We found no evidence of systematic variation in C allocation with latitude or climate (Fig. S3). Of 16 relationships tested (4 ratios among C flux variables regressed against latitude, $MAT$, $MAP$ and temperature seasonality), none were significant.
